Cocoa: Congestion Control Aware Queuing

### 2019-10-25 tex/paper.tex
Add wintracker

%\usepackage{multirow}
%\usepackage{blindtext}
%\usepackage{soul}
\usepackage{enumitem}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{subfig}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
%\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
\caption{A Cubic flow with fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be possible.}
\label{fig:fq}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we halve it after 30\,s. The delay is 10\,ms. \gls{cocoa} keeps the queue smaller than fq while achieving the same throughput.}
\label{fig:cn}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we double it after 30\,s. The delay is 10\,ms. Also a sudden large increase of bandwidth is handled well by \gls{cocoa}.}
\label{fig:cn2}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
%\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
\caption{A Cubic flow with fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.61\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 130.36\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
\caption{A BBR~v1 flow with \gls{cocoa} at the bottleneck. The bandwidth is 50\,Mbit/s. The delay is 10\,ms and we halve it after 30\,s.}
\label{fig:cnBBR}
\end{figure}

>>>>

\usepackage{enumitem}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{subfig}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
%\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
\caption{A Cubic flow with fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be possible.}
\label{fig:fq}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we halve it after 30\,s. The delay is 10\,ms. \gls{cocoa} keeps the queue smaller than fq while achieving the same throughput.}
\label{fig:cn}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput2}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay2}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we double it after 30\,s. The delay is 10\,ms. Also a sudden large increase of bandwidth is handled well by \gls{cocoa}.}
\label{fig:cn2}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
%\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
\caption{A Cubic flow with fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.61\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
\caption{A Cubic flow with \gls{cocoa} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 130.36\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputBBR}
%]{
\includegraphics[width=\columnwidth]{{{plots/throughput_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayBBR}
%]{
\includegraphics[width=\columnwidth]{{{plots/rtt_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
\caption{A BBR~v1 flow with \gls{cocoa} at the bottleneck. The bandwidth is 50\,Mbit/s. The delay is 10\,ms and we halve it after 30\,s.}
\label{fig:cnBBR}
\end{figure}
